---
title: "Predicting type of activity"
author: "Olga Illarionova"
date: "December 26, 2015"
output: html_document
---

I download data and required libraries.
```{r warning=FALSE}
library(caret)
library(dplyr)
set.seed(91)
test <- read.csv("pml-testing.csv")
train <- read.csv("pml-training.csv")
```

First of all I clean data. I remove columns where more than 95% values were missing. Also I remove column "X" just because it is convinient to me. I pdivide big training set for two sets: training and validation sets.
```{r warning=FALSE}
inTrain <- createDataPartition(y=train$classe,
                               p=0.7, list=FALSE)
train2 <- train %>% select( which(colMeans(is.na(.)) < 0.95))
train2 <- train2 %>% select( which(colMeans(train2=="") < 0.95), -X )
train2 <- train2[inTrain,]
testing <- train2[-inTrain,]

```

Then I made some preprocess with my data. I made principal component analysys with threshold of captured variance equal to 0.9.
```{r warning=FALSE}
preProc <- preProcess(train2,method="pca",thresh = 0.9)
#newTrain <- training[,c(ilp,diagnosis)]
trainPC <- predict(preProc,train2)
testPC <- predict(preProc,testing)

```
Then I created model. I use method treebag in caret package. I chose this method because it gets good accuracy and don't takes much time.
```{r warning=FALSE}
modelFitPC <- train(classe ~ .,method="treebag",data=trainPC)

```


Accuracy of my model on training set is 0.98.
```{r warning=FALSE}
tttr<- confusionMatrix(train2$classe,predict(modelFitPC,trainPC))
tttr
```

Accuracy of my model on validation set is 0.95.
```{r warning=FALSE}
ttts<- confusionMatrix(testing$classe,predict(modelFitPC,testPC))
ttts
```
I calculate missclassifiction rate using following formula:
```{r warning=FALSE}
missClass = function(values,prediction){
      sum(prediction != values)/length(values)}
#training set missclassification
mtr<- missClass(trainPC$classe,predict(modelFitPC,trainPC))
mtr
#testing (validation) set missclassification
mts<- missClass(testPC$classe,predict(modelFitPC,testPC))
mts
```

